A Grimm idea

### 2016-05-05 presentation/main.tex
projection done

\begin{frame}
  \frametitle{Locality gadget}
  \begin{itemize}
    \item Replace edge by a $p$-barrier
    \item Enforce \enquote{locality} of pebbles
    \item An agent cannot traverse any gadget without all his pebbles
    \item All pebbles of the agent are either carried or placed within the
      adjacent gadgets
  \end{itemize}
  \begin{center}
    \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/locgadget}}}
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{Barrier construction}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Locality gadget}
  \begin{itemize}
    \item Replace edge by a $(p-1)$-barrier
    \item Enforce \enquote{locality} of pebbles
    \item An agent cannot traverse any gadget without \emph{all} his pebbles
    \item All pebbles of the agent are either carried or placed within the
      adjacent gadgets
  \end{itemize}
  \begin{center}
    \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/locgadget}}}
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{Barrier construction: Initial thoughts}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Consider a subset of pebbles of cardinality $p$
      \item Use the locality gadget as edges
      \item Since pebbles are local: enumerate configurations in macro vertex
        $C_{1},\dots,C_{\alpha}$
      \item Project $A$ to a agent without pebbles $B$
      \item $B$ has $\alpha$ states and traverses through macro vertices
    \end{itemize}
    \column{0.5\textwidth}
    \resizebox{\textwidth}{!}{\input{tikz/projection}}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Barrier construction: The real deal}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item $B$ has no pebbles and is therefore prone to a $0$-barrier
    \end{itemize}
    \column{0.5\textwidth}
  \end{columns}
\end{frame}
